Clonal interference between aneuploidy and mutation

### 2021-02-10 ms/ms.tex
revised ISF ack
moved bib library
fix library path
update authors, acks, affil

\author[a]{Ilia Kohanovski}
\author[b,c]{Avihu H. Yona}
\author[d]{Orna Dahan}
\author[d]{Yitzhak Pilpel}
\author[a,*]{Yoav Ram}

\affil[a]{School of Computer Sciences, IDC Herzliya, Herzliya 4610101, Israel}
\affil[b]{Department of Physics, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}{
\affil[b]{Department of Biological Engineering, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
\affil[d]{Department of Molecular Genetics, Weizmann Institute of Science, Rehovot 76100, Israel}
\affil[*]{Corresponding author: yoav@yoavram.com}

@@

\pagebreak
% Acknowledgements
{\small
\section*{Acknowledgements}
We thank Lilach Hadany, Judith Berman, David Gresham, and Martin Kupiec for discussions and comments.
This work was supported in part by 
the Israel Science Foundation (YR 552/19).
}

\bibliographystyle{agsm}
\bibliography{/Users/yoavram/library.bib}

>>>>

\author[1]{Ilia Kohanovski}
%\author[b,c]{Avihu H. Yona}
%\author[d]{Orna Dahan}
%\author[d]{Yitzhak Pilpel}
\author[1,2,*]{Yoav Ram}

\affil[1]{School of Computer Sciences, IDC Herzliya, Herzliya, Israel}
\affil[2]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
%\affil[b]{Department of Physics, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}{
%\affil[b]{Department of Biological Engineering, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
%\affil[d]{Department of Molecular Genetics, Weizmann Institute of Science, Rehovot 76100, Israel}
\affil[*]{Corresponding author: yoav@yoavram.com}

@@

\pagebreak
% Acknowledgements
{\small
\section*{Acknowledgements}
We thank Lilach Hadany, Judith Berman, David Gresham, and Martin Kupiec for discussions and comments.
This work was supported in part by 
the Israel Science Foundation 552/19 and Minerva
Stiftung Center for Lab Evolution (YR).
}

\bibliographystyle{agsm}
\bibliography{ms.bib}
